---
title: "<TODO: TITLE>"
description: |
  <TODO: one paragraph — the question, why it matters, framed for a public
  reader who hasn't seen the site before. Pull this from the user's answer
  to the Motivation prompt, don't paraphrase it away.>
date: today
bibliography: <NAME>_data/references.bib
format:
  html:
    code-fold: true
    toc: true
    toc-depth: 2
execute:
  echo: true
  message: false
  warning: false
---

```{r}
#| label: setup
#| echo: false

library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(plotly)

theme_set(theme_minimal(base_size = 13))
irw_blue <- "#2166ac"
irw_red  <- "#d73027"
irw_grey <- "grey50"

`%||%` <- function(a, b) if (is.null(a)) b else a

cache_path <- "<NAME>_data/<NAME>_results.rds"
cache_ok   <- file.exists(cache_path)

if (cache_ok) {
  .cache           <- readRDS(cache_path)
  summary_df       <- .cache$summary
  candidate_tables <- .cache$candidate_tables
  date_run         <- .cache$date_run
  is_pilot         <- isTRUE(.cache$pilot)
  r_all_candidates <- .cache$n_all_candidates %||% length(candidate_tables)
  r_n_tables_run   <- length(candidate_tables)
  # TODO(agent): pull any other keyed objects the compute script saved
  # (e.g. .cache$eigenvalues, .cache$q3_matrices) needed for sanity-check figures.
} else {
  summary_df <- tibble(
    table = character(), n_items = integer(), n_participants = integer()
    # TODO(agent): match this empty-schema fallback to the real summary_df
    # columns the compute script writes, so the page doesn't error on a
    # missing cache.
  )
  candidate_tables <- character()
  date_run         <- Sys.Date()
  is_pilot         <- FALSE
  r_all_candidates <- 0L
  r_n_tables_run   <- 0L
}

knitr::opts_chunk$set(eval = cache_ok)
```

```{r}
#| label: cache-warning
#| echo: false
#| eval: true
#| output: asis

if (!cache_ok) cat(
  "::: {.callout-warning}\n",
  "**Cache not found** — figures and tables will not appear. Generate results ",
  "by running the compute script, then re-render:\n\n",
  "```r\nRscript vignettes/<NAME>_compute.R\n```\n",
  ":::\n", sep = ""
)
```

```{r}
#| label: pilot-warning
#| echo: false
#| eval: true
#| output: asis

if (cache_ok && is_pilot) cat(
  "::: {.callout-warning}\n",
  "**Draft preview, partial run.** This render uses a partial sample of ",
  r_n_tables_run, " tables out of ", r_all_candidates, " eligible tables, ",
  "to validate the pipeline and page layout before the full batch finishes. ",
  "All numbers here are real computed results -- not placeholders -- but ",
  "treat the *distributions* as a small, noisy preview rather than a ",
  "representative picture. Re-run `<NAME>_compute.R` (with `PILOT <- FALSE` ",
  "and the full batch complete) to scale up.\n",
  ":::\n", sep = ""
)
```

::: {.callout-note}
This vignette — including the dataset search, the compute script, the
analysis design, and the writing below — was produced largely by Claude
(Anthropic), working from a task specification and with human review.
Treat the methodological choices and interpretations accordingly, and
check the compute script (`<NAME>_compute.R`) directly if you're relying
on the numbers here.
:::

<!--
TODO(agent): if this vignette was NOT substantially authored by an
automated agent, delete the callout-note block above rather than leaving a
false disclosure in place.
-->

## Motivation

<TODO: the modeling assumption or research question, why it matters, and
links to sibling vignettes that share the assumption or method (use real
`[text](other_vignette.qmd)` links — check which ones actually exist in
vignettes/ before citing them).>

## Data and methods

### Dataset selection

```{r}
#| label: filter-datasets
#| eval: false

all_candidates <- irw_filter(
  n_items        = c(<MIN_ITEMS>, <MAX_ITEMS>),
  n_participants = c(<MIN_PARTICIPANTS>, Inf)
)
```

<TODO: why these thresholds — trace back to the user's selection-criteria
answer, not a plausible-sounding guess.> `r r_all_candidates` tables met
this criterion as of `r format(date_run, "%B %Y")`.
`r if (is_pilot) "This page currently runs on a small pilot subset (see the warning above); a full pass analyzes all of them." else paste0("This pass analyzes all ", r_n_tables_run, " of them.")`

### Per-table computation

For each candidate table, `<TODO: fit function name from the compute script>()`:

<TODO: numbered list of what the fit function actually does, matching its
real steps in `<NAME>_compute.R` — don't describe a method that isn't in
the script.>

```{r}
#| label: fit-function
#| eval: false

# TODO(agent): paste the real (trimmed) fit function body from
# <NAME>_compute.R here, not a paraphrase.
```

Of the `r r_n_tables_run` candidate tables in this pass, `r nrow(summary_df)`
produced usable results.

::: {.callout-note}
To reproduce with current IRW holdings, re-run `<NAME>_compute.R`
and commit the updated `<NAME>_data/<NAME>_results.rds`.
:::

## Results

<TODO: figures/tables built from `summary_df`. Use `ggplot2` + `ggplotly()`
with a `text=` tooltip aesthetic (showing table name) for anything with
more than one dataset per point; `knitr::kable()` for tables.>

## Limitations

<TODO: real methodological caveats grounded in what the compute script
actually does/doesn't handle — not boilerplate. Get this from the user's
Limitations-grounding answer.>

## Reproducibility

Results were computed on `r format(date_run, "%B %d, %Y")`. To regenerate:

```r
# 1. Re-run the compute script (from the project root)
source("vignettes/<NAME>_compute.R")

# 2. Re-render this page
quarto::quarto_render("vignettes/<NAME>.qmd")
```

::: {.callout-tip}
To cite the datasets used, run:

```r
irw_save_bibtex(summary_df$table, output_file = "<NAME>_data/references.bib")
```
:::

---

## References
